---
title: "Analise dos CRAS"
author: "Ricardo Lovatel"
date: "19 de outubro de 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Capa (slide inicial com título e nome)

- Objeto (tema central da apresentação)

- Objetivos (questões de pesquisa que o trabalho irá responder)

- Contexto (justificativa)

- Método (como foram coletados, tratados e organizados os dados)

- Gráficos/tabelas (2 slides, pelo menos)

- Conclusões
## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

